---  
title: HDR Attributes
date: "Updated: `r format(Sys.time(), '%d %B %Y')`"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

# Overview

  * The HDR attribute names for CAS_04 are very different from the original specifications.
  * The HDR attributes table for CAS_04 consists of three rows, one per inventory_standard_code.
  * It probably easiest to create this table manually since there is no need to loop over all records:
    - CAS_04 table: data/cas04_hdr.csv
    - CAS_05 table: data/cas05_hdr.csv
  * Do we still want one row per inventory standard?
  * Have the photoyear_start and photoyear_end dates changed?

# Attributes {.tabset}

## CAS_04

```{r echo=FALSE, message=FALSE, warning=FALSE}  
z = read_csv("data/cas04_hdr.csv") %>% filter(header_id %in% c("BC_0004","BC_0005","BC_0006"))
dfSummary(z, graph.col=FALSE, valid.col=FALSE)
```

## CAS_05

```{r echo=FALSE, message=FALSE, warning=FALSE}  
z = read_csv("data/cas05_hdr.csv") %>% filter(header_id=="BC08")
dfSummary(z, graph.col=FALSE, valid.col=FALSE)
```
