---  
title: "ON02 Inventory"
date: "Updated: `r format(Sys.time(), '%d %B %Y')`"
output:  
  html_document:  
    toc: true
    toc_float:
      collapsed: true
    code_folding: hide
    css: ../styles.css
---  

```{r echo=FALSE, message=FALSE, warning=FALSE}  
x=on02
```

# CAS Attributes

Descriptions are taken from "Forest Management Planning Technical Specification 2009"

## CAS_ID

The attribute **cas_id** attribute is a concatenation of several attributes and strings i.e., "on02", src_filename, "", polyid, ogc_fid.

## ORIG_STAND_ID

  * Source attribute: polyid
  * Description: The polygon identifier attribute is a unique identifier / label for the polygon which is often based on geographic location.

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["polyid"], graph.col=FALSE)
dfSummary(x["orig_stand_id"], graph.col=FALSE)
```

## STAND_STRUCTURE

  * source attributes: vert
  * NOTE: this attribute will be generated using SQL helper functions?

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["vert"], graph.col=FALSE)
dfSummary(x["stand_structure"], graph.col=FALSE)
```

## NUM_OF_LAYERS

  * NOTE: this attribute will be generated using SQL helper functions
  * source attributes:

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["num_of_layers"], graph.col=FALSE)
```

## IDENTIFICATION_ID

  * Source attribute: ?

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE)
#dfSummary(x["identification_id"], graph.col=FALSE)
```

## MAP_SHEET_ID

  * Source attribute: doesn't seem to exist

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=10)
#dfSummary(x["map_sheet_id"], graph.col=FALSE, max.distinct.values=10)
```

## GIS_AREA

  * Calculated by engine

## GIS_PERIMETER

  * Calculated by engin

## INVENTORY_AREA

  * Source attribute: area

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["area"], graph.col=FALSE)
dfSummary(x["inventory_area"], graph.col=FALSE)
```

## PHOTO_YEAR

  * Calculated by engine


# LYR Attributes

## SOIL_MOIST_REG

  * source attribute: doesn't seem to exist (derive from ecosite?)

## STRUCTURE_PER

  * NOTE: this attribute will be generated using SQL helper functions

## LAYER

  * NOTE: this attribute will be generated using SQL helper functions

## LAYER_RANK

  * NOTE: this attribute will be generated using SQL helper functions

## CROWN_CLOSURE

  * Source attribute: occlo, ucclo

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["occlo"], graph.col=FALSE)
dfSummary(x["crown_closure_upper"], graph.col=FALSE)
dfSummary(x["crown_closure_lower"], graph.col=FALSE)
```

## HEIGHT 

  * Source attribute: oht, uht

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["oht"], graph.col=FALSE)
dfSummary(x["height_upper"], graph.col=FALSE)
dfSummary(x["height_lower"], graph.col=FALSE)
```

## PRODUCTIVE_FOR

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["polytype"], graph.col=FALSE)
dfSummary(x["productive_for"], graph.col=FALSE)
```

## SPECIES

  * source attributes: ospcomp, uspcomp
  * needs helper function to parse string into species and species percent

## SPECIES_PER

  * source attributes: ospcomp, uspcomp
  * needs helper function to parse string into species and species percent

## ORIGIN

  * source attribute: oyrorg, uyrorg

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["oyrorg"], graph.col=FALSE)
dfSummary(x["origin_upper"], graph.col=FALSE)
dfSummary(x["origin_lower"], graph.col=FALSE)
```

## SITE_CLASS

  * source_attribute: osc, usc

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["osc"], graph.col=FALSE)
dfSummary(x["site_class"], graph.col=FALSE)
```

## SITE_INDEX

  * source_attribute: osi, usi

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["osi"], graph.col=FALSE)
dfSummary(x["site_index"], graph.col=FALSE)
```


# NFL Attributes

## SOIL_MOIST_REG

  * source attribute: doesn't seem to exist (derive from ecosite?)

## STRUCTURE_PER

  * NOTE: this attribute will be generated using SQL helper functions

## LAYER

  * NOTE: this attribute will be generated using SQL helper functions

## LAYER_RANK

  * NOTE: this attribute will be generated using SQL helper functions

## CROWN_CLOSURE

  * The CASFRI attribute is renamed to nfl_crown_closure to avoid conflict with LYR attribute of same name
  * The source attribute used is occlo (ucclo?) since NFL attributes are not distinguished by layer

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$occlo[!x$nfl_crown_closure_upper=="NULL_VALUE"], graph.col=FALSE)
dfSummary(x["nfl_crown_closure_upper"], graph.col=FALSE)
dfSummary(x$occlo[!x$nfl_crown_closure_lower=="NULL_VALUE"], graph.col=FALSE)
dfSummary(x["nfl_crown_closure_lower"], graph.col=FALSE)
```

## HEIGHT

  * The CASFRI attribute is renamed to nfl_height_uppeer to avoid conflict with LYR attribute of same name
  * The source attribute used is oht (uht?) since NFL attributes are not distinguished by layer

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$oht[!x$nfl_height_upper==-8888], graph.col=FALSE)
dfSummary(x["nfl_height_upper"], graph.col=FALSE)
dfSummary(x$oht[!x$nfl_height_lower==-8888], graph.col=FALSE)
dfSummary(x["nfl_height_lower"], graph.col=FALSE)
```

## NAT_NON_VEG

  * partial list

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["polytype"], graph.col=FALSE)
dfSummary(x["nat_non_veg"], graph.col=FALSE)
```

## NON_FOR_ANTH

  * partial list

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["polytype"], graph.col=FALSE)
dfSummary(x["non_for_anth"], graph.col=FALSE)
```

## NON_FOR_VEG

  * partial list

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["polytype"], graph.col=FALSE)
dfSummary(x["non_for_veg"], graph.col=FALSE)
```


# DST Attributes

## DIST_TYPE_1

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["devstage"], graph.col=FALSE)
dfSummary(x["dist_type_1"], graph.col=FALSE)
```

## DIST_YEAR_1

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$yrdep, graph.col=FALSE)
dfSummary(x$dist_year_1, graph.col=FALSE)
```

## DIST_EXT_UPPER_1, DIST_EXT_LOWER_1

## DIST_TYPE_2

## DIST_YEAR_2

## DIST_EXT_UPPER_1, DIST_EXT_LOWER_1

## DIST_TYPE_3

## DIST_YEAR_3

## DIST_EXT_UPPER_1, DIST_EXT_LOWER_1

## LAYER


# ECO Attributes

## WETLAND_TYPE

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["wetland_type"], graph.col=FALSE)
```

## WET_VEG_COVER

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["wet_veg_cover"], graph.col=FALSE)
```

## WET_LANDFORM_MOD

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["wet_landform_mod"], graph.col=FALSE)
```

## WET_LOCAL_MOD

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["wet_local_mod"], graph.col=FALSE)
```

## ECO_SITE

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["eco_site"], graph.col=FALSE)
```
